06-clean-data-and-frame-dict

### 2022-04-19 data-cleaning/06-clean-data-and-frame-dict.Rmd
clean search terms close #24

```{r}
frames <- box_read("947237361645")
```

@@

@@

>>>>

```{r}
# data/amicus content - frames
frames <- box_read("947237361645")
```

@@

  # Replace hyphen with space
  df$text_clean <- sapply(df$text_clean, function(x) gsub("-", " ", x))

  # Remove all other punctuation
  df$text_clean <- sapply(df$text_clean, function(x) gsub("[^[:alpha:][:space:]]", " ", x))

@@

1. One row per word/phrase

Currently, data is one row per frame. Expand df on comma

```{r}
frames <- frames %>% separate_rows(., word_list, sep = ",") %>% 
  mutate(frame_code = gsub(" ", "_", frame)) %>% 
  select(frame, frame_code, word = word_list) %>% 
  arrange(frame_code)

frames %>% head()
```

2. Fix characters

```{r}
frames <- frames %>% mutate(word_clean = fix_chars(word))
```

3. Clean text & lowercase

```{r}
# The clean_text function
clean_text_frames <- function(x) {

  # Replace contractions 
  x <- replace_contraction(x, sent.cap = FALSE)

  # Posessive words - remove 's
  x <- gsub("'s", " ", x)

  # Replace hyphen with space
  x <- gsub("-", " ", x)

  # Remove stop words
  x <- removeWords(x, words = stops)

  # Strip white space
  x <- replace_white(x)

  x <- trimws(x)

  x <- str_to_lower(x)

frames <- frames %>% mutate(word_clean = clean_text_frames(word_clean))
```

4. Fix instances where multiple phrases can come from one. Ex: "physician(s)" should be physician and physicians

Create two columns 
* tense: if a phrase includes () (example: "physician(s))
* mulit: if there are multiple tenses
* slash: if contains / (ex: "wome/an")

There are only cases with parens. No multi or slash

```{r}
frames <- frames %>%
  mutate(tense = ifelse(grepl("\\(|\\/", word_clean), word_clean, ""),
         multi = ifelse(grepl("\\)\\(", word_clean), TRUE, FALSE),
         slash = ifelse(grepl("\\/", word_clean), TRUE, FALSE)
  )

frames %>% filter(tense != "") %>% nrow()
frames %>% filter(multi) %>% nrow()
frames %>% filter(slash) %>% nrow()
```

Remove multi & slash

```{r}
frames <- frames %>% select(-multi, -slash)
```

If we have a phrase like "actually further(ed) government interest", this code chunk sets the value of `tense_1` to "actually furthered government interest" and `tense_2` to "actually further government interest."

```{r}
frames <- frames %>%
  mutate(tense_1 = ifelse(tense != "", gsub("\\(|\\)", "", word_clean), ""), 
         tense_2 = ifelse(tense != "", gsub("\\([a-z]+\\)", "", tense), ""))

# fix two errors that will arise
frames <- frames %>% 
  mutate(tense_1 = str_replace(tense_1, "uncertaintyies", "uncertainties"),
         tense_1 = str_replace(tense_1, "authorityies", "authorities"))
```

Re-apply processing on tense_1 & 2

```{r}
frames <- frames %>% mutate_at(vars(tense_1, tense_2), clean_text_frames)
```

Fix so one row per phrase

```{r}
frame_tense_1 <- frames %>% 
  filter(tense != "") %>% 
  select(frame, frame_code, word, word_clean=tense_1)

frame_tense_2 <- frames %>% 
  filter(tense != "") %>% 
  select(frame, frame_code, word, word_clean=tense_2)

frames <- frames %>% filter(tense == "") %>% select(frame, frame_code, word, word_clean)

frames <- frames %>% rbind(frame_tense_1, frame_tense_2) %>% arrange(frame, word_clean)
```

Remove any remaining punctuation

```{r}
# Remove all other punctuation
frames <- frames %>% mutate(word_clean = gsub("[^[:alpha:][:space:]]", " ", word_clean))
```

Check

```{r}
frames <- frames %>% distinct(frame, frame_code, word, word_clean)
```

```{r}
box_write(frames,
           file_name = "clean-amicus-iv-frame-dictionary.csv",
           dir_id = 161199725595)
```
